A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-17 manuscript/reply_to_reviewers.tex

		In some systems, however, the factors affecting probabilities of co-occurrence may not be known. We therefore cannot suggest modelling co-occurrence as a panacea. Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 238).

@@

		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift). Following the Reviewer's suggestion, we have revised our manuscript to clarify our terminology. In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript. We hope that this will remove some of the confusion about whether or not modelling different components of uncertainty/sampling more is a good idea.

	8. Issue of testing hypotheses based on inputs into models

		\begin{refquote}
		Line 121.  I think one of the reason non-Bayesians' are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realise there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
		\end{refquote}

		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out). We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines 260-263). We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.

@@

	11. Scepticism about sampling requirements to be sure interactions do not occur

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn't you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed.... This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed...??
		\end{refquote}

		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.

		The Reviewer's suggestion that we might need fewer samples for species that are ``specialised or bound to interact for some other reason'' reflects a very strong prior. In this case, yes we would need fewer samples for the species concerned. With sufficiently strong priors, it is not necessary to sample at all! For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros. In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are ``bound to interact'' (or not to interact). The concept of pollination syndromes is one example - many flower visitors are less rigidly specialised on particular flower types than initially thought~\citep{Ollerton2009}. To address such ``forbidden links``, we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros. This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes. We hope that this expanded recommendation (lines 399-402) is clearer.

@@

	5. Description of causes of uncertainty poorly integrated with the case study

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. 
		\end{refquote}

		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data. Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions. This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc. A more generally-applicable approach is to test explicitly whether species always interact when co-occurring, whether interaction probability depends on the probability of co-occurrence, and whether both co-occurrence and interaction probabilities depend upon environmental conditions, as in~\citet{Gravel2018}. Note, however, that this study refers to the probability of an interaction occurring in a local realisation of a food web while we are concerned with metawebs in the present study.

		To make this clearer, we have rephrased this section and added a line (lines 65-72) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible). We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.

		\begin{quotation}
			While an observed link definitely occurred (assuming species are correctly identified), a link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig. 1). Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"
		\end{quotation}

@@

		Our mention of habitat as a factor affecting the probability of species interacting at a site was not intended to refer to species using different habitats, but rather the possibility that habitat type might affect interaction probabilities. For example, a more open patch of forest might have different interaction probabilities than a denser patch even if the same set of species use both patches. The Reviewer is clearly correct that habitat also affects which species are present at a site. We included co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence). This speaks to our point above that external factors (habitat, weather, etc.) can affect multiple levels of uncertainty at once. In fact, habitat also likely affects detection uncertainty since it is often harder to observe interactions in dense vegetation. So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour and we have revised the manuscript to steer readers away from it.

	7. Point about temporal scales of interaction

		\begin{refquote}
		L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
		\end{refquote}

		\textbf{R:} Long-term interactions may be easier to detect, but this does not necessarily translate into reduced process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section (lines 143-1246). Long-term interactions may still fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).

@@

		Perhaps more important is the effect of sampling interval. As sampling time increases toward infinity, interaction probabilities should converge to 0 or 1 with no uncertainty. As we discuss, however, sampling times are limited by resources, the trade-off between sampling a single site intensively versus many sites, etc. Any interaction could therefore occur outside of the sampling window and hence be missed.

		Lines 143-146:

		\begin{quotation}
			The probability of detecting an interaction also depends on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}. 
		\end{quotation}

@@

		\textbf{R:} We have removed much of the introductory text explaining which quantity we are most interested in ($\lambda$) and now more explicitly state our goals at the end of the introduction. We hope that the transition to the methods is now less work for a reader.

	12. Ideas presented in L209, L262, L310 are important but explained too briefly

		\begin{refquote}
		L209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310). I would have appreciated a much clearer explanation and example.
		\end{refquote}

		\textbf{R:} We are not quite sure what the Reviewer is asking here. $\alpha$ and $\beta$ truly are quite simple (as simple as the mean and standard deviation of a normal distribution) so there is not much more to say about them in themselves. We have expanded our discussion of different types of priors and how they may be obtained, and we hope that this clarifies matters for the Reviewer. We also note that a simple worked example, with accompanying R code, is provided in \emph{Appendix S4} so that readers can see exactly how to obtain $\alpha$ and $\beta$. In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines 185-188) spelling this out.

		\begin{quotation}
			The shape parameters, or hyperparameters, may be set to particular values or derived from data (see below). They may be the same for all interactions, allowed to vary independently across interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
			\end{quotation}

@@

	13. Reframe line 241 in terms of solutions rather than difficulties

		\begin{refquote}
		L241 I wonder if you could phrase this more positively as `solutions' rather than just `difficulties'?
		\end{refquote}

		\textbf{R:} We appreciate the Reviewer's desire for optimism and have tried to reframe the manuscript in order to present Bayesian approaches as a partial solution to problems of uncertainty.
